Joint training of classification model and similarity model for low-resource text classification in chatbot

### 2020-07-26 chatbot_classification/aaai_2021/paper.tex
modified:   paper.pdf   modified:   paper.tex   modified:   picture1.key   modified:   picture1.pdf   modified:   picture2.key

\begin{figure}[htbp]
\centering 
\subfigure[text classification model structure based on pre-trained transformer]{
\label{Fig.1.sub.1}
\includegraphics[scale=0.6]{picture1.pdf}}
\subfigure[sentence-pair model structure based on cross-attention mechanism]{
\label{Fig.1.sub.2}
\includegraphics[scale=0.55]{picture2.pdf}}
\caption{Model Structure of 2 popular approach for building task-specific conversational chatbot}
\label{Fig.1.main}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering 
\subfigure[classification model]{
\label{Fig.1.sub.1}
\includegraphics[scale=0.7]{picture1.pdf}}
\subfigure[similarity model]{
\label{Fig.1.sub.2}
\includegraphics[scale=0.55]{picture2.pdf}}
\caption{Two popular structures of building task-specific conversational chatbot}
\label{Fig.1.main}
\end{figure}
